DOM Review Summary

### 2024-03-14 Analysis/ReviewSummary/ReviewSummary.qmd
Wrote outline
Generated outline for each section of the review summary, with details on available fields and required plots

---
title: "DOM Review Summary"
author: "Saoirse Kelleher"
date: "March 13 2024"
date-modifed: today
abstract: "A summary of results from the DOM Review, for use in interpreting outputs and writing the review manuscript. "
abstract-title: "Summary"
format: 
  html:
    theme: minty
    toc: true
---

@@

| Field             | Description                                      | Possible values                      |
|--------------|------------------------------------|----------------------|
| Journal           | Journal which this article was published in      | *Any*                                |
| Year              | Year of publication                              | *Any*                                |
| Author country    | Nation of the first author's primary affiliation | *ISO 3166 country names*             |
| Author categories | Categories of affiliations for *all* authors     | *Academic, Government, NGO, Private* |

@@

| Objective           | Description                                                                       |
|---------------------|---------------------------------------------------|
| Methods             | Did authors seek to demonstrate or test specific methods for occupancy modelling? |
| Future Predictions  | Did authors make predictions beyond the study period?                             |
| Spatial Predictions | Did authors make predictions at locations where surveys were not conducted?       |
| Hypothesis testing  | Did authors seek to test specific hypotheses of species occupancy dynamics?       |

@@

| Field           | Description                                                                                | Possible values                                                                   |
|----------------|----------------------------|----------------------------|
| Taxa category   | Category of study taxa; could fit into multiple categories                                 | *Bird, Mammal, Invertebrate, Herptile, Fish, Threatened, Invasive, Other*         |
| Taxa number     | Number of individual species within the taxa for which models were fit                     | *Numeric*                                                                         |
| IUCN status     | IUCN status for the study species; NA if multi-species or if the study species is invasive | *LC, NT, EN, CR, DD, NA*                                                          |
| Threat category | Category of threats to the species; multiple per species permitted                         | *Habitat loss, Climate change, Exploitation, Invasives, Disease, Disaster, Other* |
| Country         | Country/countries where the study took place                                               | *ISO 3166 country names*                                                          |
| Continent       | Continent(s) where the study took place                                                    | *North America, South America, Europe, Asia, Africa, Oceania*                     |
|                 |                                                                                            |                                                                                   |
|                 |                                                                                            |                                                                                   |
|                 |                                                                                            |                                                                                   |
|                 |                                                                                            |                                                                                   |
|                 |                                                                                            |                                                                                   |

@@

##

@@

@@

>>>>

---
title: "DOM Review Summary"
author: "Saoirse Kelleher"
date: "March 13 2024"
date-modifed: today
abstract: "A summary of results from the DOM Review, for use in interpreting outputs and writing the review manuscript. "
abstract-title: "Summary"
format: 
  html:
    theme: minty
    toc: true
embed-resources: true
---

@@

+-------------------+--------------------------------------------------+--------------------------------------+
| Field             | Description                                      | Possible values                      |
+===================+==================================================+======================================+
| Journal           | Journal which this article was published in      | *Any*                                |
+-------------------+--------------------------------------------------+--------------------------------------+
| Year              | Year of publication                              | *Any*                                |
+-------------------+--------------------------------------------------+--------------------------------------+
| Author country    | Nation of the first author's primary affiliation | *ISO 3166 country names*             |
+-------------------+--------------------------------------------------+--------------------------------------+
| Author categories | Categories of affiliations for *all* authors     | *Academic, Government, NGO, Private* |
+-------------------+--------------------------------------------------+--------------------------------------+

@@

+---------------------+-----------------------------------------------------------------------------------+
| Objective           | Description                                                                       |
+=====================+===================================================================================+
| Methods             | Did authors seek to demonstrate or test specific methods for occupancy modelling? |
+---------------------+-----------------------------------------------------------------------------------+
| Future Predictions  | Did authors make predictions beyond the study period?                             |
+---------------------+-----------------------------------------------------------------------------------+
| Spatial Predictions | Did authors make predictions at locations where surveys were not conducted?       |
+---------------------+-----------------------------------------------------------------------------------+
| Hypothesis testing  | Did authors seek to test specific hypotheses of species occupancy dynamics?       |
+---------------------+-----------------------------------------------------------------------------------+

@@

+-----------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------+
| Field           | Description                                                                                | Possible values                                                                   |
+=================+============================================================================================+===================================================================================+
| Taxa category   | Category of study taxa; could fit into multiple categories                                 | *Bird, Mammal, Invertebrate, Herptile, Fish, Threatened, Invasive, Other*         |
+-----------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------+
| Taxa number     | Number of individual species within the taxa for which models were fit                     | *Numeric*                                                                         |
+-----------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------+
| IUCN status     | IUCN status for the study species; NA if multi-species or if the study species is invasive | *LC, NT, EN, CR, DD, NA*                                                          |
+-----------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------+
| Threat category | Category of threats to the species; multiple per species permitted                         | *Habitat loss, Climate change, Exploitation, Invasives, Disease, Disaster, Other* |
+-----------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------+
| Country         | Country/countries where the study took place                                               | *ISO 3166 country names*                                                          |
+-----------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------+
| Continent       | Continent(s) where the study took place                                                    | *North America, South America, Europe, Asia, Africa, Oceania*                     |
+-----------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------+
| Realm           | Biogeographic realm where the study took place                                             | *Nearctic, Palearctic, Afrotropical, Indomalayan, Australasian, Neotropical*      |
+-----------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------+
| Size            | Size of the study area extent in square kilometres                                         | *\<1km, 1-10, 10-100, 100-1000, 10000-100000, 100000-1000000, 1000000+*           |
+-----------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------------+

## Taxa categories

## Number of species

## Threatened taxa

## Study locations

@@

+---------------------+--------------------------------------------------------------------------+----------------------------------------------------------------------------------------------+
| Field               | Description                                                              | Possible values                                                                              |
+=====================+==========================================================================+==============================================================================================+
| Duration            | Length of study in months                                                | *Numeric*                                                                                    |
+---------------------+--------------------------------------------------------------------------+----------------------------------------------------------------------------------------------+
| Capture method      | Method of recording detections; multiple categories possible             | *Audiovisual, Search, Trapping, Bioacoustic, Camera, Citizen, Incidental*                    |
+---------------------+--------------------------------------------------------------------------+----------------------------------------------------------------------------------------------+
| Primary occasions   | Number of primary occasions                                              | *Numeric*                                                                                    |
+---------------------+--------------------------------------------------------------------------+----------------------------------------------------------------------------------------------+
| Secondary occasions | Number of secondary occasions, presented as a range where not consistent | *Numeric range*                                                                              |
+---------------------+--------------------------------------------------------------------------+----------------------------------------------------------------------------------------------+
| Secondary type      | Type of secondary occasion                                               | *Revisits, Spatial replicates, Same-visit replicates, multiple observers, time to detection* |
+---------------------+--------------------------------------------------------------------------+----------------------------------------------------------------------------------------------+
| Type of site        | How a 'site' was defined                                                 | *Point location, Grid cell, Irregular area, Transect*                                        |
+---------------------+--------------------------------------------------------------------------+----------------------------------------------------------------------------------------------+
| Number of sites     | Number of individual sites                                               | Numeric                                                                                      |
+---------------------+--------------------------------------------------------------------------+----------------------------------------------------------------------------------------------+
| Sampling method     | How sites were selected                                                  | *Random, Stratified, Grid, Preferential, Available, Exhaustive, Uniform, Transect*           |
+---------------------+--------------------------------------------------------------------------+----------------------------------------------------------------------------------------------+

## Study duration

## Number of occasions

## Data collection method

## Sampling method

## Study size over time

@@

All covariates considered for modelling were documented for each article. Details available for each covariate include:

+-------------+-------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Field       | Description                                     | Possible values                                                                                                                                                     |
+=============+=================================================+=====================================================================================================================================================================+
| Parameter   | Parameter which this covariate was considered   | *Initial occupancy, colonisation, extinction, detection*                                                                                                            |
+-------------+-------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Type        | Category of covariate                           | *Environmental: Habitat type terrestrial, Habitat type aquatic, Anthropogenic, Topographic, Climate and weather, Disaster and disturbance, Hydrologic, Seasonality* |
|             |                                                 |                                                                                                                                                                     |
|             |                                                 | *Other: Interactions, Site geometry, Connectivity, Site-level effects, Species-level effects, Season-level effects, Survey details*                                 |
+-------------+-------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Variation   | Level of variation for the covariate            | *Site, Season, Survey*                                                                                                                                              |
+-------------+-------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Measurement | How the covariate was recorded                  | *Remotely, Observed, Intrinsic*                                                                                                                                     |
+-------------+-------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Complexity  | How the covariate was mathmatically implemented | *Linear-only, Quadratics, Interactions, Interactions and Quadratics, Other*                                                                                         |
+-------------+-------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------+
|             |                                                 |                                                                                                                                                                     |
+-------------+-------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------+

## Covariate quantity

## Covariate categories

## Covariate features

## Frequency of covariate features

## Quantity of covariates by year

## Quantity of covariates by study size

@@

Key details of the modelling process were documented.

+---------------+-----------------------------------------------------------+-------------------------------------------------------------------------------------------------+
| Field         | Description                                               | Possible values                                                                                 |
+===============+===========================================================+=================================================================================================+
| Bayesian      | Whether the models fit were Bayesian                      | *Logical*                                                                                       |
+---------------+-----------------------------------------------------------+-------------------------------------------------------------------------------------------------+
| Prefiltering  | Which, if any, prefiltering method was used               | *Expert, Simple, Other*                                                                         |
+---------------+-----------------------------------------------------------+-------------------------------------------------------------------------------------------------+
| Selection     | Which, if any, selection method was used                  | *Single a priori, Multiple a priori, Exhaustive, Exhaustive by parameter, Forwards, Backwards*  |
+---------------+-----------------------------------------------------------+-------------------------------------------------------------------------------------------------+
| Evaluation    | How models were compared and evaluated                    | *AIC, AUC, DiC, Model-averaging, Bootstrapping*                                                 |
+---------------+-----------------------------------------------------------+-------------------------------------------------------------------------------------------------+
| Multi-species | Whether this was a multi-species model                    | *Logical*                                                                                       |
+---------------+-----------------------------------------------------------+-------------------------------------------------------------------------------------------------+
| Connectivity  | Whether site connectivity was incorporated into the model | *Logical*                                                                                       |
+---------------+-----------------------------------------------------------+-------------------------------------------------------------------------------------------------+
